---
title: "Regression on FeetApart + Sitting"
output: pdf_document
---

I first check the multicollinearity and recursively remove variables with VIF > 10. Based on the remaining variables, I perform stepwise selection and best subset selection. And if the best model results are different, I compare two models using ANOVA.

```{r}
library(car)
library(MASS)
library(leaps)
```

```{r}
# iWear
iwear <- read.csv("../../../iWear/iWear_complete_0206.csv")
df_subscore <- iwear[c(1,269,270)]

# APDM - standing
apdm_standing <- read.csv("../../../APDM/FAEOFirm.csv", stringsAsFactors=FALSE)
apdm_standing$X[1:20] <- paste0("IW", substr(apdm_standing$X[1:20],3,4), "GHI")
## Postural Sway - Acc - Jerk (m^2/s^5) / Postural Sway - Acc - Mean Velocity (m/s)
## Postural Sway - Acc - RMS Sway (m/s^2) / Postural Sway - Angles - Sway Area (degrees^2)
df_standing <- apdm_standing[c(1,12,15,21,30)]
colnames(df_standing) <- c("as_correct",
                           "Jerk_Standing","Mean_Velocity_Standing",
                           "RMS_Sway_Standing","Sway_Area_Standing")

# APDM - sitting
apdm_sitting <- read.csv("../../../APDM/Sitting Postural Sway.csv", stringsAsFactors=FALSE)
apdm_sitting$X[1:20] <- paste0("IW", substr(apdm_sitting$X[1:20],3,4), "GHI")
## Postural Sway - Acc - Jerk (m^2/s^5) / Postural Sway - Acc - Mean Velocity (m/s)
## Postural Sway - Acc - RMS Sway (m/s^2) / Postural Sway - Angles - Sway Area (degrees^2)
df_sitting <- apdm_sitting[c(1,12,15,21,30)]
colnames(df_sitting) <- c("as_correct",
                          "Jerk_Sitting","Mean_Velocity_Sitting",
                          "RMS_Sway_Sitting","Sway_Area_Sitting")

# merge
df <- merge(df_subscore, df_standing, sort = F)
df <- merge(df, df_sitting, sort = F) ## remove 8 WS
## remove control group
df <- na.omit(df) ## 20GHI+15TC
```

# Balance
```{r}
mod_balance <- lm(Balance_Subscore ~., data = df[,-c(1,3)])
summary(mod_balance)
```

## Multicollinearity
```{r}
## Recursively remove variables with VIF > 10
all_vifs <- vif(mod_balance)
print(all_vifs)

signif_all <- names(all_vifs)
while(any(all_vifs > 10)){
  var_with_max_vif <- names(which(all_vifs == max(all_vifs))) ## get the var with max VIF
  signif_all <- signif_all[!(signif_all) %in% var_with_max_vif] ## remove
  myForm <- as.formula(paste("Balance_Subscore ~ ", paste (signif_all, collapse=" + "), sep="")) ## new formula
  mod_balance_vif <- lm(myForm, data = df) ## re-build model with new formula
  all_vifs <- vif(mod_balance_vif)
}
print(all_vifs)

summary(mod_balance_vif)
```

## Stepwise Selection
```{r}
## Fit the full model
full.mod_balance <- lm(Balance_Subscore ~ Jerk_Standing + Mean_Velocity_Standing + Sway_Area_Standing + Jerk_Sitting + Mean_Velocity_Sitting + Sway_Area_Sitting, data = df)

## Stepwise regression model
step.mod_balance <- stepAIC(full.mod_balance, direction = "both", trace = FALSE)
summary(step.mod_balance)
```

## Best Subset Selection
```{r}
regsubsetsObj <- regsubsets(x=df[,c(4,5,7,8,9,11)] ,y=df$Balance_Subscore, nbest = 2, really.big = T)
plot(regsubsetsObj, scale = "adjr2")  
```

```{r}
mod1 <- lm(Balance_Subscore ~ Jerk_Standing, data = df)
mod2 <- lm(Balance_Subscore ~ Jerk_Standing + Mean_Velocity_Standing, data = df)
anova(mod1,mod2)
```
### For the p-value is 0.1813, the mod2 is not significantly different from mod1. Therefore, the best model is Balance_Subscore ~ Jerk_Standing.

# Chore
```{r}
mod_chore <- lm(Chore_Subscore ~., data = df[,-c(1,2)])
summary(mod_chore)
```

## Multicollinearity
```{r}
## Recursively remove variables with VIF > 10
all_vifs <- vif(mod_chore)
print(all_vifs)

signif_all <- names(all_vifs)
while(any(all_vifs > 10)){
  var_with_max_vif <- names(which(all_vifs == max(all_vifs))) ## get the var with max VIF
  signif_all <- signif_all[!(signif_all) %in% var_with_max_vif] ## remove
  myForm <- as.formula(paste("Chore_Subscore ~ ", paste (signif_all, collapse=" + "), sep=""))  ## new formula
  mod_chore_vif <- lm(myForm, data = df) ## re-build model with new formula
  all_vifs <- vif(mod_chore_vif)
}
print(all_vifs)

summary(mod_chore_vif)
```

## Stepwise Selection
```{r}
## Fit the full model
full.mod_chore <- lm(Chore_Subscore ~ Jerk_Standing + Mean_Velocity_Standing + Sway_Area_Standing + Jerk_Sitting + Mean_Velocity_Sitting + Sway_Area_Sitting, data = df)

## Stepwise regression model
step.mod_chore <- stepAIC(full.mod_chore, direction = "both", trace = FALSE)
summary(step.mod_chore)
```

## Best Subset Selection
```{r}
regsubsetsObj <- regsubsets(x=df[,c(4,5,7,8,9,11)] ,y=df$Chore_Subscore, nbest = 2, really.big = T)
plot(regsubsetsObj, scale = "adjr2")
```

### The best model is Chore_Subscore ~ Sway_Area_Standing + Jerk_Sitting.