---
title: "IPD"
output: pdf_document
---

```{r}
df <- read.csv("datasets/imp_1.csv")
```

## Density Plot
```{r}
library(ggplot2)
ggplot(df, aes(x=modmotscpost, colour=Group)) + geom_density()
```

## Pre-Processing & Functions
```{r}
# Group: 1-intervention 2-control
# df$Group <- as.integer(df$Group)
index <- c(0,1)
values <- c("control", "intervention")
df$Group <- index[match(df$Group, values)]

# Gender: 1-female 2-male
# df$Gender <- as.integer(df$Gender)
index <- c(0,1)
values <- c("female", "male")
df$Gender <- index[match(df$Gender, values)]
```

```{r}
ovlp <- function(trt, lps)
{
  ## This function displays an overlap histogram for "lps" across "trt" groups
  ## Statistical test of mean difference
  tt <- t.test(x = lps[trt==1], y = lps[trt==0], alternative = "two.sided",
               var.equal = FALSE)$p.value
  ## Statistical test of difference in distribution
  ks <- ks.test(x = lps[trt==1], y = lps[trt==0], alternative = "two.sided")$p.value
  
  par(mfrow = c(2,1))
  rc <- range(lps)
  brks <- seq(from = rc[1] - diff(rc)/20, to = rc[2] + diff(rc)/20, by = diff(rc)/20)
  hist(lps[trt==1], breaks = brks, xlab = "", main = "Treated Cases",
       freq = FALSE)
  d1 <- density(lps[trt==1])
  lines(d1, col = 2, lwd = 1, lty = 1)
  abline(v = c(range(lps[trt==1])), col = 3, lty = 2)
  hist(lps[trt==0], breaks = brks, xlab = "", main = "Control Cases",
       freq = FALSE)
  d2 <- density(lps[trt==0])
  lines(d2, col = 2, lwd = 1, lty = 1)
  abline(v = c(range(lps[trt==0])), col = 3, lty = 2)
  par(mfrow = c(1,1))
}

## Note that ovlp_ind requires that package optmatch be loaded
ovlp_ind <- function(trt, lps, caliper = 0.1)
{
  nt <- sum(trt == 1); nc <- sum(trt == 0)
  SDpool <- sqrt( ( (nt - 1)*var(lps[trt == 1]) + (nc - 1)*var(lps[trt == 0]) ) / 
                    (nt + nc - 2) )
  ## Get abs(distance) for each treat/control pairing
  diffs <- match_on(trt ~ lps, method = "euclidean")
  smds <- diffs/SDpool # standardize differences by dividing by pooled SD
  fun <- function(vec) {min(vec) <= caliper}
  trtOvlp <- apply(smds, 1, fun)   # TRUEs are overlapping
  ctrlOvlp <- apply(smds, 2, fun)  # FALSEs are not
  drop1 <- which(trt==1)[!trtOvlp]
  drop0 <- which(trt==0)[!ctrlOvlp]
  ind <- !logical(length(lps))
  ind[c(drop1, drop0)] <- FALSE
  ind
}
```

## Simple Difference in Means
First, we check the normality of the data.
```{r}
shapiro.test(df$modmotscpost)
```
For the p-value is larger than 0.05, we fail to reject H0, that is the distribution of the data are not significantly different from normal distribution. In other words, we can assume the normality.

Then, we use Bartlett’s test to check homogeneity of variances.
```{r}
bartlett.test(modmotscpost ~ Group, data = df)
```
For the p-value is larger than 0.05, we fail to reject H0, that is the variance in modmotscpost is not significantly different between groups.

Finally, we perform the t-test to obtain p-value and confidence interval.
```{r}
pfe <- t.test(x = with(df, modmotscpost[Group == 0]),
              y = with(df, modmotscpost[Group == 1]),
              var.equal = TRUE,
              conf.int = TRUE)
diff(pfe$estimate)
pfe$conf.int
pfe$p.value
```

## Propensity Scores 
```{r}
## Estimate propensity scores with logistic regression
glm1 <- glm(Group ~ Age + Gender + modmotscpre + EQ5Dpre + TFC + UHDRStV1 +SDMTpre,
            data = df, family = "binomial")
ps1 <- predict(glm1, type = "response")
lin_ps1 <- log(ps1/(1 - ps1))

## Assess overlap
ovlp(trt = df$Group, lps = lin_ps1)
```

### .2 caliper
```{r}
## Create overlap indicator
library(optmatch)
library(survival)
ovlp_ind1 <- ovlp_ind(trt = df$Group, lps = lin_ps1, caliper = .2) # requires optmatch
sum(ovlp_ind1)
table(ovlp_ind1, df$Group)

## Solve margin error
par(mar=c(1,1,1,1))

## Examine overlap after eliminating non-overlapping cases
ovlp(trt = df$Group[ovlp_ind1], lps = lin_ps1[ovlp_ind1])
```

### .25 caliper
```{r}
## Create overlap indicator
library(optmatch)
library(survival)
ovlp_ind1 <- ovlp_ind(trt = df$Group, lps = lin_ps1, caliper = .25) # requires optmatch
sum(ovlp_ind1)
table(ovlp_ind1, df$Group)

## Solve margin error
par(mar=c(1,1,1,1))

## Examine overlap after eliminating non-overlapping cases
ovlp(trt = df$Group[ovlp_ind1], lps = lin_ps1[ovlp_ind1])
```

### .3 caliper
```{r}
## Create overlap indicator
library(optmatch)
library(survival)
ovlp_ind1 <- ovlp_ind(trt = df$Group, lps = lin_ps1, caliper = .3) # requires optmatch
sum(ovlp_ind1)
table(ovlp_ind1, df$Group)

## Solve margin error
par(mar=c(1,1,1,1))

## Examine overlap after eliminating non-overlapping cases
ovlp(trt = df$Group[ovlp_ind1], lps = lin_ps1[ovlp_ind1])
```

## Regression Estimation
```{r}
dat <- df[,-c(1:3,13)]

## Create a data subset for group 1 - intervention
dat1 <- subset(dat, subset = dat$Group == 1)
dim(dat1)

## Create a data subset for group 0 - control
dat0 <- subset(dat, subset = dat$Group == 0)
dim(dat0)

## Regression model for group 1 
lmY1 <- lm(modmotscpost ~ . - Group, data = dat1)
summary(lmY1)

## Regression model for group 0
lmY0 <- lm(modmotscpost ~ . - Group, data = dat0)
summary(lmY0)

## ATE
Y1hats <- predict(lmY1, newdata = df)
Y0hats <- predict(lmY0, newdata = df)
(ATE_RE <- mean(Y1hats - Y0hats))

## ATT
Y0hatsATT <- predict(lmY0, newdata = dat1)
(ATT_RE <- mean(dat1$modmotscpost - Y0hatsATT))
```