---
title: "iWear Falls and Lifespace Analyses"
output: 
  pdf_document:
    toc: true
---

\newpage

```{r}
library(knitr)
library(ggplot2)
library(car)
library(MASS)
library(leaps)
df <- read.csv("iWear_complete_0625.csv")
fields <- colnames(df)
```

# 1. Falls - Descriptive Analysis (History of Falls Questionnaire)
## Number of fallers (hfq_2)
```{r}
# grep("hfq_2",fields) # 83
sum(df$hfq_2, na.rm = T)
```

## Number of falls (hfq_2_yes, mean, median, min, max)
```{r}
summary(df$hfq_2_yes)
```

## Description of most common activity at the time of fall (hfq_3, frequency distribution)
```{r}
# table(df$hfq_3)
df_hfq_3 <- data.frame(c(1,14,1,2,2,1,8),
                       row.names = c("running","walking","standing",
                                     "getting in/out of bed, chair wheelchair, car",
                                     "climbing on/off chair, stool, ladder",
                                     "participating in sports/exercising, dancing/riding a bicycle",
                                     "other"))
colnames(df_hfq_3) <- "frequency"
kable(df_hfq_3)
```

## Cause of fall (hfq_4, frequency distribution)
```{r}
# grep("hfq_4___1",fields) # 87
df_hfq_4 <- data.frame(colSums(df[,c(87:107)], na.rm = T))
rownames(df_hfq_4) <- c("legs gave way", "dizzy", "light-headed", 
                        "weak", "passed out", "loss of balance", 
                        "paralysis weakness", "quick movement",  
                        "dual task motor (carrying an object)",
                        "dual task cognitive (ie. walking while talking)",
                        "tripped stumbled", "slipped", "missed seat",
                        "was bumped/pushed", "slid off surface", "bumped into object",
                        "furniture/equipment broke", "physical fatigue", "mental fatigue",
                        "uncertain", "other")
colnames(df_hfq_4) <- "frequency"
kable(df_hfq_4)
```

## Location of fall (hfq_5, frequency distribution)
```{r}
# table(df$hfq_5)
df_hfq_5 <- data.frame(c(15,2,12),
                       row.names = c("inside home","inside another building","outside"))
colnames(df_hfq_5) <- "frequency"
kable(df_hfq_5)
```

## Contribution of environmental hazards (hfq_6, number/percentage of participants)
```{r}
# number
sum(df$hfq_6, na.rm = T)
# percentage
sum(df$hfq_6, na.rm = T)/sum(df$hfq_2, na.rm = T) 
```

## Which environmental hazards contributed to falls (hfq_6_specify, frequency distribution)
```{r}
# grep("hfq_6_specify___1",fields) # 111 - 125
df_hfq_6 <- data.frame(colSums(df[,c(111:125)], na.rm = T))
rownames(df_hfq_6) <- c("icy surface", "slipper/wet surface", "uneven surface",
                        "objects on surface (stones, toys, cords)",
                        "surface color was not different to show change in level",
                        "rug (tripped, slid on it)", 
                        "steps of unequal height",
                        "darkness/dimness of environment",
                        "glare from lights of snow",
                        "furniture/stair step/ railing broke",
                        "stocking/ socks slippery",
                        "something moved and bumped me",
                        "new eyeglasses",
                        "other", "uncertain")
colnames(df_hfq_6) <- "frequency"
kable(df_hfq_6)
```

## Required help after fall (hfq_8, number/percentage of fallers hfq_2)
```{r}
# number
sum(df$hfq_8, na.rm = T)
# percentage
sum(df$hfq_8, na.rm = T)/sum(df$hfq_2, na.rm = T) 
```

## Injury after fall (hfq_9, number/percentage of fallers hfq_2)
```{r}
# number
sum(df$hfq_9, na.rm = T)
# percentage
sum(df$hfq_9, na.rm = T)/sum(df$hfq_2, na.rm = T) 
```

## Recovery after fall (hfq_13_yes, mean, median, min, max days)
```{r}
summary(df$hfq_13_yes)
```

## Most serious injury after fall (hfq_15a, frequency distribution)
```{r}
# table(df$hfq_15a)
df_hfq_15a <- data.frame(c(4,12,1,2),
                         row.names = c("cut, laceration",
                                       "bruise or hematoma",
                                       "sprain or strain",
                                       "fracture"))
colnames(df_hfq_15a) <- "frequency"
kable(df_hfq_15a)
```

## Location of most serious injury (hfq_15b, frequency distribution)
```{r}
# table(df$hfq_15b)
df_hfq_15b <- data.frame(c(5,1,1,3,1,1,1,1,1,1,1),
                         row.names = c("head", "face", "upper arm",
                                       "elbow", "lower arm", "hand","back",
                                       "knee", "lower leg", "ankle",
                                       "other"))
colnames(df_hfq_15b) <- "frequency"
kable(df_hfq_15b)
```

# 2. Falls - Association with Motor and Cognitive Function
## Correlation of number of falls with UHDRS total motor score (TMS)
```{r}
temp <- df[,c("hfq_2_yes","TMS")]
temp <- na.omit(temp) 
ggplot(temp) +
  geom_point(aes(x = hfq_2_yes, y = TMS)) +
  labs(title = "Correlation of number of falls with TMS",
       subtitle = cor(temp$hfq_2_yes, temp$TMS))
```

## Correlation of number of falls with UHDRS cognitive (sdm_correct, sdm_errors)
```{r}
# sdm_correct
temp <- df[,c("hfq_2_yes","sdm_correct")]
temp <- na.omit(temp) 
ggplot(temp) +
  geom_point(aes(x = hfq_2_yes, y = sdm_correct)) +
  labs(title = "Correlation of number of falls with sdm_correct",
       subtitle = cor(temp$hfq_2_yes, temp$sdm_correct))

# sdm_errors
temp <- df[,c("hfq_2_yes","sdm_errors")]
temp <- na.omit(temp) 
ggplot(temp) +
  geom_point(aes(x = hfq_2_yes, y = sdm_errors)) +
  labs(title = "Correlation of number of falls with sdm_errors",
       subtitle = cor(temp$hfq_2_yes, temp$sdm_errors))
```

# 3. Falls - Association with Physical Activity
## Correlation of number of falls with percentage of sedentary time
```{r}
temp <- df[,c("as_correct","hfq_2_yes","sed_perc")]
temp <- na.omit(temp) 
ggplot(temp, aes(x = hfq_2_yes, y = sed_perc, label = as_correct)) +
  geom_point() +
  geom_text(aes(label = as_correct), size = 2, hjust = 0, vjust = 0) +
  labs(title = "Correlation of number of falls with percentage of sedentary time",
       subtitle = cor(temp$hfq_2_yes, temp$sed_perc))

# significance level
cor.test(temp$hfq_2_yes, temp$sed_perc)
```
The p-value is 0.5327, which is larger than the significance level 0.05. We can conclude that number of falls and percentage of sedentary time are not significantly correlated.

## Correlation of number of falls with total sway area 
```{r}
df_sway <- read.csv("../APDM/Sitting Postural Sway.csv", header=T, stringsAsFactors=FALSE)[,c(1,30)]
colnames(df_sway) <- c("as_correct", "total_sway_area")
df_sway$as_correct[1:20] <- paste0("IW",substr(df_sway$as_correct[1:20],3,4),"GHI")
df <- merge(df, df_sway, all.x = T)

temp <- df[,c("hfq_2_yes", "total_sway_area")]
temp <- na.omit(temp) # n = 19
ggplot(temp) +
  geom_point(aes(x = hfq_2_yes, y = total_sway_area)) +
  labs(title = "Correlation of number of falls with total sway area",
       subtitle = cor(temp$hfq_2_yes, temp$total_sway_area))

# significance level
cor.test(temp$hfq_2_yes, temp$total_sway_area)
```
The p-value is 0.188, which is larger than the significance level 0.05. We can conclude that number of falls and total sway area are not significantly correlated.

# 4. Falls - Regression
```{r}
lm_falls <- lm(hfq_2_yes ~ TMS + sdm_correct + total_sway_area + Avg_Daily_StepCount, data = df)
summary(lm_falls)

# multicollinearity
vif(lm_falls)
temp <- df[,c("TMS", "sdm_correct")]
cor.test(temp$TMS, temp$sdm_correct)

# stepwise selection
step.lm_falls <- stepAIC(lm_falls, direction = "both", trace = FALSE)
summary(step.lm_falls)

# best subset selection
temp <- df[,c("hfq_2_yes","TMS", "sdm_correct", "total_sway_area", "Avg_Daily_StepCount")]
temp <- na.omit(temp) # n = 11
regsubsetsObj <- regsubsets(x=temp[,c("TMS", "sdm_correct", "total_sway_area", "Avg_Daily_StepCount")],
                            y=temp$hfq_2_yes, nbest = 2, really.big = T)
plot(regsubsetsObj, scale = "adjr2")  

# 
cor.test(temp$hfq_2_yes, temp$total_sway_area) # significantly correlated
```

# 5. Lifespace - Frequency Distribution
```{r}
df_ls <- data.frame(table(df$ls_score))
colnames(df_ls) <- c("ls","frequency")
kable(df_ls)
```

# 6. Lifespace - Association with Disease Severity
## Correlation of lifespace score with UHDRS total motor score (TMS)
```{r}
temp <- df[,c("ls_score","TMS")]
temp <- na.omit(temp) 
ggplot(temp) +
  geom_point(aes(x = ls_score, y = TMS)) +
  labs(title = "Correlation of lifespace score with TMS",
       subtitle = cor(temp$ls_score, temp$TMS))
```

# 7. Lifespace- Association with Balance and Physical Activity
## Correlation of lifespace score with balance subscore
```{r}
temp <- df[,c("ls_score","Balance_Subscore")]
temp <- na.omit(temp) 
ggplot(temp) +
  geom_point(aes(x = ls_score, y = Balance_Subscore)) +
  labs(title = "Correlation of lifespace score with balance subscore",
       subtitle = cor(temp$ls_score, temp$Balance_Subscore))
```

## Correlation of lifespace score with self-reported physical activity (ipaq_score_post)
```{r}
temp <- df[,c("ls_score","ipaq_score_post")]
temp <- na.omit(temp) 
ggplot(temp) +
  geom_point(aes(x = ls_score, y = ipaq_score_post)) +
  labs(title = "Correlation of lifespace score with self-reported physical activity",
       subtitle = cor(temp$ls_score, temp$ipaq_score_post))
```

## Correlation of lifespace score with actual physical activity average step counts
```{r}
temp <- df[,c("as_correct","ls_score","Avg_Daily_StepCount")]
temp <- na.omit(temp) 
ggplot(temp, aes(x = ls_score, y = Avg_Daily_StepCount, label = as_correct)) +
  geom_point() +
  geom_text(aes(label = as_correct), size = 2, hjust = 0, vjust = 0) +
  labs(title = "Correlation of lifespace score with with average step counts",
       subtitle = cor(temp$ls_score, temp$Avg_Daily_StepCount))
```

## Correlation of lifespace score with percentage of sedentary time
```{r}
temp <- df[,c("as_correct","ls_score","sed_perc")]
temp <- na.omit(temp) 
ggplot(temp, aes(x = ls_score, y = sed_perc, label = as_correct)) +
  geom_point() +
  geom_text(aes(label = as_correct), size = 2, hjust = 0, vjust = 0) +
  labs(title = "Correlation of lifespace score with percentage of sedentary time",
       subtitle = cor(temp$ls_score, temp$sed_perc))

# significance level
cor.test(temp$ls_score, temp$sed_perc)
```
The p-value is 0.6873, which is larger than the significance level 0.05. We can conclude that number of falls and total sway area are not significantly correlated.

## Correlation of lifespace score with total sway area
```{r}
temp <- df[,c("ls_score","total_sway_area")]
temp <- na.omit(temp)
ggplot(temp) +
  geom_point(aes(x = ls_score, y = total_sway_area)) +
  labs(title = "Correlation of lifespace score with total sway area",
       subtitle = cor(temp$ls_score, temp$total_sway_area))

# significance level
cor.test(temp$ls_score, temp$total_sway_area)
```
The p-value is 0.005826, which is less than the significance level 0.05. We can conclude that lifespace score and total sway area are significantly correlated with a correlation coefficient of -0.67.

# 8. Lifespace - Association with Cognitive and Behavioral Function
## Correlation of lifespace score with Symbol Digit Modality Test correct score 
```{r}
temp <- df[,c("ls_score","sdm_correct")]
temp <- na.omit(temp) 
ggplot(temp) +
  geom_point(aes(x = ls_score, y = sdm_correct)) +
  labs(title = "Correlation of lifespace score with sdm_correct",
       subtitle = cor(temp$ls_score, temp$sdm_correct))
```

## Correlation of lifespace score with Symbol Digit Modality Test error score
```{r}
temp <- df[,c("ls_score","sdm_errors")]
temp <- na.omit(temp) 
ggplot(temp) +
  geom_point(aes(x = ls_score, y = sdm_errors)) +
  labs(title = "Correlation of lifespace score with sdm_errors",
       subtitle = cor(temp$ls_score, temp$sdm_errors))
```
        
## Correlation of lifespace score  with Verbal Fluency Test score
```{r}
temp <- df[,c("as_correct","ls_score","vf_subtotal")]
temp <- na.omit(temp) 
ggplot(temp, aes(x = ls_score, y = vf_subtotal, label = as_correct)) +
  geom_point() +
  geom_text(aes(label = as_correct), size = 2, hjust = 0, vjust = 0) +
  labs(title = "Correlation of lifespace score with vf_subtotal",
       subtitle = cor(temp$ls_score, temp$vf_subtotal))
```

# 9. Lifespace - Association with Functional Limitations
## Correlation of lifespace score with Total Functional Capacity score (TFC)
```{r}
temp <- df[,c("as_correct","ls_score","TFC")]
temp <- na.omit(temp) 
ggplot(temp, aes(x = ls_score, y = TFC, label = as_correct)) +
  geom_point() +
  geom_text(aes(label = as_correct), size = 2, hjust = 0, vjust = 0) +
  labs(title = "Correlation of lifespace score with TFC",
       subtitle = cor(temp$ls_score, temp$TFC))
```

## Correlation of lifespace score with Functional Assessment (FA)
```{r}
temp <- df[,c("as_correct","ls_score","FA")]
temp <- na.omit(temp) 
ggplot(temp, aes(x = ls_score, y = FA, label = as_correct)) +
  geom_point() +
  geom_text(aes(label = as_correct), size = 2, hjust = 0, vjust = 0) +
  labs(title = "Correlation of lifespace score with FA",
       subtitle = cor(temp$ls_score, temp$FA))
```

# 10. Lifespace - Regression
```{r}
lm_ls <- lm(ls_score ~ sdm_correct + TMS + total_sway_area, data = df)
summary(lm_ls)

# multicollinearity
vif(lm_ls)

# stepwise selection
step.lm_ls <- stepAIC(lm_ls, direction = "both", trace = FALSE)
summary(step.lm_ls)

# best subset selection
temp <- df[,c("ls_score","TMS", "sdm_correct", "total_sway_area")]
temp <- na.omit(temp) # n = 14
regsubsetsObj <- regsubsets(x=temp[,c("TMS", "sdm_correct", "total_sway_area")],
                            y=temp$ls_score, nbest = 2, really.big = T)
plot(regsubsetsObj, scale = "adjr2")  

# 
cor.test(temp$ls_score, temp$total_sway_area) # significantly correlated
```

# 11. Correlation of Lifespace with Falls
```{r}
temp <- df[,c("ls_score","hfq_2_yes")]
temp <- na.omit(temp)
ggplot(temp) +
  geom_point(aes(x = ls_score, y = hfq_2_yes)) +
  labs(title = "Correlation of lifespace score with number of falls",
       subtitle = cor(temp$ls_score, temp$hfq_2_yes))

# significance level
cor.test(temp$ls_score, temp$hfq_2_yes)
```
The p-value is 0.2996, which is larger than the significance level 0.05. We can conclude that lifespace score and number of falls are not significantly correlated.